\documentclass[11pt,fleqn]{article}

\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{url}

\setlength {\topmargin} {-.15in}
\setlength {\textheight} {8.6in}

\input{simple-type-theory-def}
\input{alonzo-notation}

% Credit to Gabriel Devenyi for this bibliography cfg:
% github.com/gdevenyi/mcmaster.latex
\usepackage[
  style=numeric-comp,
  backend=biber,
  sorting=none,
  backref=true,
  maxnames=99,
  alldates=iso,
  seconds=true
]{biblatex} % bibliography
\addbibresource{references.bib}

\begin{document}

\thispagestyle{empty}

\bc
  {\large \textbf{CAS 760}}\\[2mm]
  {\large \textbf{Logic for Practical Use}}\\[2mm]
  {\large \textbf{Fall 2022}}\\[8mm]
  {\huge \textbf{Development Project: Continuity on Topological Partial Algebras}}\\[6mm]
  {\large \textbf{Zheheng Zhao and Fateme Ghasemi }}\\[2mm]
  {\large \textbf{McMaster University}}\\[6mm]
  {\large {\today}}

\ec
\newpage
\tableofcontents
\newpage
%------------------------------------------------------------------------------
% Introduction
%------------------------------------------------------------------------------
\section{Introduction}
%----------------------------------
% Introduction
%----------------------------------
While-Computability is a fundamental model for imperative programming on any data type.
Continuous data types are modeled by topological many-sorted algebras.
The topology defines a concept of closeness and hence the process of approximation for data.

\section{Topological algebra}
% Topological algebra helps convert topological problems into algebraic problems which are easier to solve in practice.
Topological algebra is an algebra which is also a topological space at same time.

\begin{df}
    A topological algebra over a topological field is a topological vector space together with a bilinear operation that is continuous in some definite sense.
\end{df}

\subsection{Topological algebra in Alonzo}
\begin{theory-def}{Topological algebra}
    {$\mName{TOP-ALG}$.}
    {A}
    {$\cup_{\cFunTyBX {A}{A}{A}}$, $\cap_{\cFunTyBX {A}{A}{A}}$.}
    {
    \be
        \item $\emptyset_{\{ A\} } \in \mName{ISOPEN} $
        \hfill (Empty set is in the collection of open sets).
        \item  $U_{ \{ A\} } \in \mName{ISOPEN} $ \hfill (The base set itself is in the collection of open sets).
        % \item  Any (finite or infinite) union of sets that are open is itself open
        \item $\cForallX {a_i}{A} (a_i \in \mName{ISOPEN}) \Rightarrow (\bigcup a_i \in \mName{ISOPEN})$ 
        % \item  Any finite intersection of sets that are open is itself open
        \item $\cForallX {a_i}{A} ((a_i \in \mName{ISOPEN}) \land (i \neq \infty)) \Rightarrow (\bigcap a_i \in \mName{ISOPEN})$
    \ee
    }
\end{theory-def}

\section{What is a Topological Partial Algebra?}

\begin{df}
% A Topological Partial Algebra $\mathbb{A} = (A, (f_i)_{i \in I})$ is a
% partial algebra with topologies on
% carriers such that each of the basic functions $f_i$ is 
% \textcolor{teal}{continuous} on the product topology.
A Topological Partial Algebra is a partial algebra with topologies on carriers such that each of the basic functions $f$ is \textcolor{teal}{continuous} on the product topology.
\end{df}

\begin{df}
  % A function $f:X \rightarrow Y $ is continuous if the pre-image of every open set in $Y$ is \textcolor{teal}{open} in $X$. 
  A function $f$ is continuous if the pre-image of every open set in its range is open in its domain.
\end{df}

\begin{df}
  % a function $f$ is open if $\forall V : Y \rightarrow \omicron \cdot V \in \mName{ISOPEN} \Rightarrow (\mName{PREIMAGE}(f)) (V) \in$ ISOPEN.
  a function $f$ is open if its domain is open implies the range of its pre-image is also open.
\end{df}

\subsection{Topological partial algebra in Alonzo}

  \begin{theory-ext}{Topological partial algebra}
    {$\mName{TOP-PAR-ALG}$.}
    {$\mName{TOP-ALG}$.}
    {I}
    {$(f_i : A^{\alpha_i} \rightarrow A^{\beta_i} )_{i \in I}$,PREIMAGE$_{ (A \rightarrow A) \rightarrow \{ A \} \rightarrow \{ A \}}$.}
    {
    \be \setcounter{enumi}{4}
        \item $\cForallX {V}{\cFunTyX{A}{\omicron}} V \in \mName{ISOPEN} \Rightarrow \mName{PREIMAGE(V)} \in \mName{ISOPEN}$ 
        \hfill (Continuity).
        \item $\cForallX {i}{I} \cIsDefX{\mName{PREIMAGE} (i, \alpha_i, \beta_i)}$
        \item PREIMAGE = $\cFunAbsX {i} {I} {} \cFunAbsX {\alpha_i, \beta_i} {N} {} \cFunAbsX {f} {\cFunTyX{A^{\alpha_i}}{A^{\beta_i}}} {} \cFunAbsX {V} {\cFunTyX{A^{\beta_i}}{\omicron}} {} \cDefDesX {K} {\cFunTyX{A^{\alpha_i}}{\omicron}} {} \cForallX {x}{K} \cAndX {\cIsDefX{f(x)}} {\cup_{x\in K} f(x) = V}$
    \ee
    }
\end{theory-ext}

\begin{cor}
  Note that since ISOPEN is defined as a predicate, it is total, and hence is defined for any subset of the base set.
\end{cor}
 
%------------------------------------------------------------------------------
% Bibliography
%------------------------------------------------------------------------------
\begin{thebibliography}{1}
  \bibitem{1} Tucker, J V, and J I Zucker, 'Computable functions and semicomputable sets on many-sorted algebras', in S Abramsky, Dov M Gabbay, and T S E Maibaum (eds), Handbook of Logic in Computer Science: Volume 5. Algebraic and Logical Structures (Oxford, 2001; online edn, Oxford Academic, 12 Nov. 2020), \url{https://doi.org/10.1093/oso/9780198537816.003.0005}
  \bibitem{2} Farmer, W, 'Simple Type Theory A Practical Logic for Expressing and Reasoning about Mathematical Ideas'
  \bibitem{3} J.V. Tucker, J.I. Zucker, 'Computation by ‘While’ programs on topological partial algebras', Theoretical Computer Science, Volume 219, Issues 1–2, 1999, Pages 379-420, ISSN 0304-3975, \url{https://doi.org/10.1016/S0304-3975(98)00297-7}

  \end{thebibliography}

\printbibliography[heading=bibintoc]

\end{document}